Survey Results from: Meta-analytic approaches and new effect sizes to account for heterogeneous effects in comparative physiology

### 2021-07-21 R/survey_data_results.Rmd
Survey results and vis update

pacman::p_load(dplyr,ggplot2,here, pander, janitor, magrittr)

@@

# ggplot2 theme for plots
background.colour <- "white"
text.colour <- "black"
# Font Choice
#loadfonts()
text.font <- "Arial"

tm <- theme(panel.background = element_rect(fill = background.colour),
            plot.background = element_rect(fill = background.colour),
            panel.grid = element_blank(),
            text =  element_text(family = text.font, colour = text.colour),
            axis.text = element_text(colour = text.colour),
            axis.title.x = element_text(margin = margin(10,0,0,0)),
            axis.title.y = element_text(margin = margin(0,10,0,0)),
            axis.line = element_line(colour = text.colour, size = 0.5),
            axis.ticks = element_line(colour = text.colour, size = 0.5),
            plot.title = element_text(hjust = 0.5),
            legend.background = element_rect(fill = background.colour),
            legend.key = element_rect(fill = background.colour),
            plot.margin = margin(6,6,6,6)) 
```

@@

summary %>% 
  ggplot() + tm +
  geom_col(aes(x = effect, y = prop), width = 0.5, fill = "black", colour = text.colour, size = 0.5) +
  scale_y_continuous(expand=c(0,0),limits = c(0,0.4)) +
  labs(x = "Analytical Approach",
       y = "Frequency") +
  coord_flip()
```

@@

>>>>

pacman::p_load(dplyr,ggplot2,here, pander, janitor, magrittr,ggalluvial,ggpubr)

@@

# ggplot2 theme for plots
background.colour <- "white"
text.colour <- "black"
# Font Choice
#loadfonts()
text.font <- "Helvetica"
line.width <- 0.6

tm <- theme(panel.background = element_rect(fill = background.colour),
            plot.background = element_rect(fill = background.colour),
            panel.grid = element_blank(),
            text =  element_text(family = text.font, colour = text.colour),
            axis.text = element_text(colour = text.colour),
            axis.title.x = element_text(margin = margin(10,0,0,0)),
            axis.title.y = element_text(margin = margin(0,10,0,0)),
            axis.line = element_line(colour = text.colour, size = line.width),,
            axis.ticks = element_line(colour = text.colour, size = line.width),
            plot.title = element_text(hjust = line.width),
            legend.background = element_rect(fill = background.colour),
            legend.key = element_rect(fill = background.colour),
            plot.margin = margin(6,6,6,6))

tm2 <- theme(panel.background = element_rect(fill = background.colour),
            plot.background = element_rect(fill = background.colour),
            panel.grid = element_blank(),
            text =  element_text(family = text.font, colour = text.colour, size = 15),
            axis.text = element_text(colour = text.colour),
            axis.text.y = element_text(angle = 90, vjust = 0.5, hjust = 0.5),
            axis.title.x = element_text(margin = margin(10,0,0,0)),
            axis.title.y = element_text(margin = margin(0,10,0,0)),
            axis.line = element_line(colour = text.colour, size = line.width),,
            axis.ticks = element_line(colour = text.colour, size = line.width),
            plot.title = element_text(hjust = line.width),
            legend.background = element_rect(fill = background.colour),
            legend.key = element_rect(fill = background.colour),
            plot.margin = margin(15,15,15,15))
```

@@

summary %>% 
  ggplot() + tm +
  geom_col(aes(x = effect, y = prop), width = 0.5, fill = background.colour, colour = text.colour, size = 0.5) +
  scale_y_continuous(expand=c(0,0),limits = c(0,0.4)) +
  labs(x = "Analytical Approach",
       y = "Frequency") +
  coord_flip()
```

@@

### Synthetic plot

```{r}
plot1 <- dat %>% 
  ggplot() + tm2 + theme(legend.position = "top") +
  geom_bar(aes(x = comparative_physiology_main_focus,
               fill = cont_moderator_variable,
               y = ..count../sum(..count..)), width = 0.5,
           colour = NA, size = 0.5) +
  scale_y_continuous(expand=c(0,0)) +
  scale_fill_brewer(palette = "Set2") +
  labs(x = "Main focus on comparative physiology",
       y = "Number of papers",
       fill = "Continuous predictor present")
plot1

plot2 <- dat %>% 
  ggplot() + tm2 + theme(legend.position = "top") +
  geom_bar(aes(x = pub_year,
               fill = meta_analysis_self_described,
               y = ..count../sum(..count..)), width = 0.5,
           colour = NA, size = 0.5) +
  scale_y_continuous(expand=c(0,0)) +
  scale_fill_brewer(palette = "Set2") +
  labs(x = "Year of publication",
       y = "Number of papers",
       fill = "Meta-analysis")
plot2

plot3 <- dat %>%
  ggplot(mapping = aes(x = comparative_physiology_main_focus,
               y = meta_analysis_self_described)) + tm2 +
  theme(panel.border = element_rect(size = 0.5, fill = NA),
        panel.grid.major = element_line(colour = "grey92"),
        axis.text.y = element_text(angle = 90)) +
  geom_count(mapping = aes(size = ..n.., colour = "A")) +
  scale_size_continuous(range = c(20,40), guide = F) +
  scale_colour_brewer(palette = "Set2", guide = F) +
  # scale_y_continuous(expand=c(0,0)) +
  # scale_fill_viridis_d() +
  labs(x = "Main focus on comparative physiology",
       y = "Number of papers")
plot3

plot4 <- dat %>%
  ggplot(aes(axis1 = meta_analysis_self_described,
             axis2 = comparative_physiology_main_focus,
             axis3 = cont_moderator_variable)) +
  ggalluvial::geom_alluvium(aes(fill = comparative_physiology_main_focus), width = 1/4, alpha = 0.8) +
  tm2 + theme(axis.line = element_blank(), axis.ticks = element_blank()) +
  theme(legend.position = "none", panel.grid = element_blank(), axis.text.y = element_blank()) +
  scale_fill_brewer(palette = "Set2") +
  ggalluvial::geom_stratum(fill = 'white', colour = 'black', width = 1/4) +
  geom_text(stat = 'stratum',
            aes(label = after_stat(stratum)),
            # label = c('weighted', 'unweighted', 'unclear'),
            colour = 'black') +
  scale_x_discrete(expand = c(.1, .1), limits = c("Meta-analysis", "Comparative physiol.", "Cont. moderator"))
plot4

panels <- ggarrange(ggarrange(plot1, plot2, nrow = 1),
                    ggarrange(plot3, plot4, nrow = 1, widths = c(1,2)),
                    nrow = 2, ncol = 1)
ggsave(panels, filename = "multipanel.pdf", device = "pdf")

```
